Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

\begin{figure}
	\includegraphics[width=\linewidth]{bfs_speedup_over_graphs.jl.png}
	\includegraphics[width=\linewidth]{bellmanford_speedup_over_graphs.jl.png}
    \caption{Performance of graph apps across various tools.}
\end{figure}

>>>>

\changwan{explain roadnet and scale free graphs here}
To evaluate the capabilities of Finch in graph applications, we its performance for two fundamantal graph applications: Breadth-first search (BFS) and Bellman-Ford single-source shortest path. We For scale-free graphs where the distribution of node degrees follows a power-law distribution and a diameter is very short, direction-optimization~\cite{} is crucial to achiceve high-performance. Direction-optimized BFS uses push and pull traversal to efficiently explore graphs. Push traversal starts from the source node, pushing neighboring nodes into the queue. Pull traversal starts from the target node, exploring predecessors (parents). This approach uses early-break in pull traversal, which is used to terminate the traversal prematurely once the target node is encountered, to avoid unnecessary edge traversal.

Figure~\cite{graph_result} (a) \changwan{add (a) in fig} shows BFS speedup over Graphs.jl, a BFS implementation with push traversal of Julia. `finch\_push\_only` only uses push traversal, whereas `finch\_push\_pull` applies direction-optimization used in GraphBLAS. As shown in Figure~\cite{graph_result} (a), direction-optimization significantly improves the performance for scale-free graphs.

\begin{figure}
	\includegraphics[width=\linewidth]{bfs_speedup_over_graphs.jl.png}
	\includegraphics[width=\linewidth]{bellmanford_speedup_over_graphs.jl.png}
    \caption{Performance of graph apps across various tools.}
     \label{graph_result}
\end{figure}
